Xolotl: An Intuitive and Approachable Neuron \& Network Simulator in MATLAB

### 2018-06-08 paper/paper.tex
fig1 done

\begin{figure}
	\centering
	\includegraphics[width=1.0\linewidth]{gfx/figure_HH}
	\caption{\texttt{xolotl} can quickly set up and simulate conductance-based models. (A) Cartoon of a Hodgkin-Huxley single-compartment neuron model with fast sodium, delayed rectifier, and leak currents. (B) Code snippet in \texttt{MATLAB} used to implement D, F-I. (C) \texttt{xolotl} schematic displayed in the \texttt{MATLAB} command prompt. (D) Simulated voltage trace of a Hodgkin-Huxley model with three conductances and 0.2 nA of injected current. Colors indicate the dominant current (gold is fast sodium, blue is delayed rectifier, red is leak). (E) Firing rate-input relation displaying firing rate as a function of injected current current. (F-G) Steady-state gating functions for activation (m) and inactivation (h) gating variables. (H-I) Voltage-dependence of time constants for activation (m) and inactivation (h) gating variables.}
	\label{fig:figurehh}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=1.0\linewidth]{gfx/figure_HH}
	\caption{\texttt{xolotl} can quickly set up and simulate conductance-based models. Schematic representation of a electrotonically-neuron with three populations of ion channels (colored rectangles). In the simulator, the soma is represented using ab object of class $compartment$ and the populations of ion channels are represented by $conductance$ objects contained within the compartment. Code snippet used to set up this neuron model, inject current, integrate and plot the voltage, and show activation functions demonstrates how various several steps can be run in a few lines of code. (A) Simulated voltage trace of a Hodgkin-Huxley model with three conductances and 0.2 nA of injected current. Colors indicate the dominant current (gold is fast sodium (NaV), blue is delayed rectifier (Kd), red is Leak). (C) f-I curve of this neuron. (D-E) Steady-state gating functions for activation (m) and inactivation (h) gating variables. (F-I) Voltage-dependence of time constants for activation (m) and inactivation (h) gating variables}
	\label{fig:figurehh}
\end{figure}
